Domain Specific Language for high performance computing

### 2024-02-05 paper/paper.tex
implementing last cse when simd
write paper at Code generate section

\documentclass[ams, a4j]{U-AizuGT}
\usepackage{pifont}
% \usepackage{graphicx}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{listings,jvlisting}
% \documentclass[a4j]{jarticle} %ここは関係ない
\usepackage{listings,jvlisting} 
\usepackage[dvipdfmx]{graphicx}
\lstset{
    frame=single,
    numbers=left,
    tabsize=2
}

@@

test

@@

\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
int kernel(EPI epi, EPJ epj, FORCE force, double eps2, int n){
	// (1).preprocess
	for(int i = 0;i < n;i += 1) {
		// (2).load EPI 
		// (3).Initialization of tmporary force
		for(int j = 0;j < n;j += 1) {
				// (4). calculate interparticle interactions
		}
		// (5). Store calculation result in the FORCE
	}
}
\end{lstlisting}

@@

\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
EPI.pos vec3<F64> xi
EPJ.pos vec3<F64> xj
EPJ.m F64 mass
FORCE.acc vec3<F64> ai
F64 eps2
F64 g
dr = xj - xi
ai = g * mass *  dr / sqrt(dr ** 2 + eps2) ** 3
\end{lstlisting}
\subsection{Implementation}
The process of generating code is illustrated in the following flowchart. In Parsing, the information
of the variables defined in the DSL code is converted into a hash with the variable names as keys. 
Formulas are converted into syntax trees using the sympify() method of Sympy, and a list of these 
trees is obtained. Next, Common Subexpression Elimination (CSE) is performed on the syntax trees of the converted formulas. CSE is the process 
of reducing the number of operations by pre-calculating common subexpressions in formulas and using 
their results in subsequent calculations. In type inference, the types of the primary variables in the 
formulas are inferred. Afterward, all syntax trees are converted into binary trees to align them with 
SIMD operations. Finally, the code for calculating interactions is generated by traversing the processed 
syntax trees. The following sections describe how the implementation was carried out in the order of
Parsing, CSE, type inference, conversion to binary trees, and Code generation.
% \includegraphics[width=\columnwidth]{flowchartver3.jpg}
\subsubsection{Parsing}
In Parsing, the process is divided between variable definition and formula handling. In variable definition, 
objects with class, vector, type, and variable name are created respectively. A hash with the variable name
as the key is then made (name\_variable\_map). Formulas use the sympify() method from the Sympy library to convert
the code read as a string into a syntax tree of formulas, obtaining a list of these syntax trees (expr\_list). Next, 
Common Subexpression Elimination (CSE) is performed.
\subsubsection{CSE}

@@

\subsection{Experiments}

>>>>

\documentclass[ams, a4j]{U-AizuGT}
\usepackage{pifont}
% \usepackage{graphicx}
\usepackage{cite}
\usepackage{mathtools}
% \usepackage{listings,jvlisting}
% \documentclass[a4j]{jarticle} %ここは関係ない
\usepackage{listings,jvlisting} 
\usepackage[dvipdfmx]{graphicx}
\lstset{
    frame=single,
    numbers=left,
    tabsize=2
}

@@

@@

\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
int kernel(double xi[][3], double xj[][3], double ai[][3], double eps2, int n){
	// (1).preprocess
	for(int i = 0;i < n;i += 4) {
		// (2).load EPI 
		// (3).Initialization of tmporary force
		for(int j = 0;j < n;j += 1) {
				// (4). calculate interparticle interactions
		}
		// (5). Store calculation result in the FORCE
	}
}
\end{lstlisting}

@@

\begin{lstlisting}[frame=single, caption=hoge, label=fuga]
EPI.pos vec3<F64> xi
EPJ.pos vec3<F64> xj
EPJ.m F64 mass
FORCE.acc vec3<F64> ai
F64 eps2
F64 g
dr = xj - xi
ai = g * mass *  dr / sqrt(dr ** 2 + eps2) ** 3
\end{lstlisting}
\subsection{Implementation}
The process of generating code is illustrated in the following flowchart. In Parsing, the information
of the variables defined in the DSL code is converted into a hash with the variable names as keys. 
Formulas are converted into syntax trees using the sympify() method of Sympy, and a list of these 
trees is obtained. Next, Common Subexpression Elimination (CSE) is performed on the syntax trees of the converted formulas. CSE is the process 
of reducing the number of operations by pre-calculating common subexpressions in formulas and using 
their results in subsequent calculations. In type inference, the types of the primary variables in the 
formulas are inferred. Afterward, all syntax trees are converted into binary trees to align them with 
SIMD operations. Finally, the code for calculating interactions is generated by traversing the processed 
syntax trees. The following sections describe how the implementation was carried out in the order of
Parsing, CSE, type inference, conversion to binary trees, and Code generation.
\includegraphics[width=\columnwidth]{flowchartver3.jpg}
\subsubsection{Parsing}
In Parsing, the process is divided between variable definition and formula handling. In variable definition, 
objects with class, vector, type, and variable name are created respectively. A hash with the variable name
as the key is then made (name\_variable\_map). Formulas use the sympify() method from the Sympy library to convert
the code read as a string into a syntax tree of formulas, obtaining a list of these syntax trees (expr\_list). Next, 
Common Subexpression Elimination (CSE) is performed.
\subsubsection{CSE}

@@

\begin{lstlisting}[frame=single, caption=hoge]
//(1) include part
#include<math>
#include<immintrin.h>
int kernel( (2) double xi[][3], double xj[][3], double eps2 ...) {
  //(3) decleare tmp variable
  int i;
  int j;
  __m256d xi_tmp_v0;
  __m256d xi_tmp_v1;  
  __m256d xi_tmp_v2;
  __m256d eps2_tmp;
  . 
  .
  .

  // (4) loop increment
  for(i = 0;i < (n);i += 4) {
    // (5) Load EPI variable part and initialize result temporary variable
      int index_gather_0[4] = {0, 3, 6, 9};
      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
      .
      .
      .

    for(j = 0;j < (n);j += 1) {
      // (6) Load EPJ variable part
         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);

      // (7) calculate interparticle
    }

    // (8) Store result part

  }
  return 0;
}

\end{lstlisting}

\section{Experiments}
